Update and evaluation of the ozone dry deposition in the Oslo~CTM3 v1.0

### 2019-07-09 DryDep.tex
Spell-checked.

\subsubsection{Aerodynamic resistance}
\label{subsubsec:Ra}
In general, the aerodynamic resistance describes the turbulent transport of any substance down to the surface. To derive $R_a^k$, we follow \citet{WASP:Simpson2003,ACP:Simpson2012} and compute a local friction velocity at reference height $z_\mathrm{ref}$ \citep[Eq.~(52),][]{ACP:Simpson2012}
\begin{equation}
  u_*^k = \frac{\overline{u}(z_\mathrm{ref})\cdot\kappa}{\ln{(\frac{z_\mathrm{ref}-d_k}{z_0^k})}-\Psi_m(\frac{z_\mathrm{ref}-d_k}{L})+\Psi_m(\frac{z_0^k}{L})},
  \label{eq:local_fric_vel}
\end{equation}
with the average wind speed $\overline{u}(z_\mathrm{ref})$ at reference height, the K\'{a}rm\'{a}n constant $\kappa = 0.40$, the integrated stability equation for momentum $\Psi_m$ \citep[e.g.,][]{Garratt1992}, a grid average Obukhov length $L$, deplacement height $d_k$, and roughness length $z_0^k$ ($d_k=0.78\cdot h_k(\mathrm{lat})$, $z_0^k=0.07\cdot h_k(\mathrm{lat})$ for forests, $d_k=0.7\cdot h_k(\mathrm{lat})$, $z_0^k=0.1\cdot h_k(\mathrm{lat})$ for vegetation other than forests). Concidering the height of vegetation, we have chosen the model level such that $\overline{z}_\mathrm{ref}\approx 45\,\unit{m}$. Using the derived $u_*^k$ from Eq.~(\ref{eq:local_fric_vel}), a local Obukhov length $L_k$ can be obtained from \citep[Eq.~(8),][]{ACP:Simpson2012}:
\begin{equation}
  L_k = - \frac{\rho c_p T_\mathrm{2m} u_*^k}{\kappa g H}.
\end{equation}
Herein, $H$ is the sensible heat flux, $g$ is the standard gravitational acceleration, $c_p$ the specific heat capacity, and $T_{2m}$ the $2\,\unit{m}$ temperature. With these, we can compute the aerodynamical resistance for each land surface type \citep[Eq.~(8.8),][]{WASP:Simpson2003}
\begin{equation}
  R_a^k = \frac{1}{\kappa u_*^k}\left[{\ln{\left(\frac{z_\mathrm{ref}-d_k}{z_0^k}\right)}-\Psi_h\left(\frac{z_\mathrm{ref}-d_k}{L_k}\right)+\Psi_h\left(\frac{z_0^k}{L_k}\right)}\right],
\end{equation}
with the integrated stability equation for heat $\Psi_h$ \citep[e.g.,][]{Garratt1992}. Both integrated stability functions ($\Psi_m$, $\Psi_h$) and corresponding parameters are listed in supplement~S.1.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-laminar layer resistance}
\label{subsubsec:Rb}
The quasi-laminar layer resistance $R_b^{i,k}$ is species specific and differs over land and ocean surfaces.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over land, we use \citep[Eq.~(53),][]{ACP:Simpson2012}
\begin{equation}
  R_b^{i,k} = \frac{2}{\kappa u_*} \cdot \left(\frac{\text{Sc}_i}{\text{Pr}}\right)^{\frac{2}{3}},
  \label{eq:Rb}
\end{equation}
wherein $\text{Pr}$ is the Prandtl number (0.72 for air and other gases) and $\text{Sc}_i$ is the Schmidt number for a gas $i$. Eq.~(\ref{eq:Rb}) differs from a similar formulation in \citet{ACP:Seinfeld2006} by a factor of roughly $1.25$. From $\text{Sc}_i = \nu/D_i$, with the kinematic viscosity of air $\nu$, we derive a Schmidt number in water equivalent:
\begin{equation}
  \text{Sc}_i = \frac{D_\chem{H_2O}}{D_i} \cdot \text{Sc}_\chem{H_2O},
\end{equation}
with the molecular diffusivity for any gas $D_i$, the Schmidt number of water ($\text{Sc}_\chem{H_2O}=0.6$) and its molecular diffusivity ($D_\chem{H_2O}=0.21\cdot10^{-4}\,\unit{m^2\,s^{-1}}$). The used ratios $D_\chem{H_2O}/D_i$ are taken from \citet[][Table S18]{ACP:Simpson2012}.\\

@@

Dry deposition velocities are directly available only for the new model version. For \emph{Wesely\_type}, monthly averaged dry deposition velocities $v^\chem{O_3}_\text{DD}$ had to be retrospectively estimated from the ratio between the total ozone dry deposition $\sum \chem{O_3^\text{DD}}(z_0)$ and monthly averaged ozone amount in the lowermost modellevel $\chem{O_3}(p_0)$ 
\begin{equation}
  v^\chem{O_3}_\text{DD} = \frac{\sum \chem{O_3^\text{DD}}(z_0)}{\chem{O_3}(p_0)}\cdot c_\text{month}.
  \label{eq:retro_vdd}
\end{equation}
Herein, $c_\text{month} = \frac{\Delta h_\text{month}}{s_\text{month}}$, with the monthly average height of the lowermost model level in each gridbox $\Delta h_\text{month}$ and the respective number of seconds in a month $s_\text{month}$. In case of \emph{mOSaic}, Eq.~(\ref{eq:retro_vdd}) yields similar values for $v^\chem{O_3}_\text{DD}$ as directly available from model output.
%
\subsubsection{Zonal distribution}
\label{subsubsec:zonal}
%
The annual zonal average with respect to surface ozone concentration (Fig.~\ref{fig:mmm_drydep}a) displays on average, in consistency with Fig.~\ref{fig:diff_maps}a, a global increase of surface ozone concentrations by $6\,\unit{ppb}$ comparing \emph{mOSaic} to \emph{Wesely\_type}. This increase is largest in the zonal band $(25-50)\,\unit{^\circ N}$ which contains the major deserts. In the deep tropics ($5\,\unit{^\circ S}-5\,\unit{^\circ N}$), the increase is smallest ($\mathcal{O}(5\,\unit{ppb})$). We find that the mOSaic scheme further intensifies the strong asymmetry between northern and southern hemisphere as a consequence of the distribution of the continental land masses and vegetation thereon. Among the sensitivity studies focusing on the stomatal conductance, there is only a low absolute variance. Neglecting the dependence on light in the stomatal conductance formulation (\emph{mOSaic\_offLight}) -- or in other words allowing photosynthesis 24/7 -- decreases the ozone concentration by $1-2\,\unit{ppb}$ in the tropics and NH mid latitudes, while choosing soil water at shallower depths (\emph{mOSaic\_SWVL1}) increases $[\chem{O_3}]$ insignificantly. Rather surprisingly, switching off the phenology completely (\emph{mOSaic\_offPhen}) amounts on average only to small difference ($\mathcal{O}(<1\,\unit{ppb})$). Most remarkable, but expected due to the much smaller prescribed dry deposition velocity over ice and snow, \emph{mOSaic\_ice} displays a doubling of surface ozone in the high Arctics compared to \emph{Wesely\_type} ($\mathcal{O}(20\,\unit{ppb})$) but affects ozone concentrations down to latitudes at about $50\,\unit{^\circ}$ in both hemispheres. Reducing $R^\chem{O_3}_\text{desert}$ by $60\,\unit{\%}$ (\emph{mOSaic\_desert}) a reduction in the order of $1\,\unit{ppb}$ is found mainly limited to the NH. The largest impact on ozone concentrations ($\mathcal{O}(2-5\,\unit{ppb})$) is found for the experiment \emph{mOSaic\_hough} which is closest to \emph{Wesely\_type}, since we used on average the same $R^\chem{O_3}$ (see Supplement~S.7). The scenario of differing emissions (2005 in comparison to 2014 or more specifically \emph{mOSaic} compared to \emph{mOSaic\_emis2014}), yields higher ozone concentrations in the northern hemisphere in 2005 in accordance to a reduction in sulfur and \chem{NO_x} emissions in south east Asia in later years. An opposite tendency is seen for latitudes south of $30\,\unit{^\circ N}$, where an increase in ozone precursors is seen in CEDS.

@@

Table~\ref{tab:trop_ozone_burden} displays the average tropospheric ozone burden for all model experiments. Consistently with the previous findings, the mOSaic scheme increases the tropospheric ozone burden by about $35\,\unit{Tg}$. From various satellite ozone retrieval products, \citet[][Tab.~5]{ESA:Gaudel2018} deduce a lower limit estimate for global tropospheric ozone burden for the years $2010-2014$ of $333-345\,\unit{Tg}$, but remark that this amount underestimates the actual tropospheric ozone burden, since it is only based on daytime retrievals. Nevertheless, the results of \emph{mOSaic} lie $17\,\unit{\%}$ above that estimate and also well above the typical modeling range of $302-378\,\unit{Tg}$ \citep{ACP:Young2013}. The difference between \emph{mOSaic} and \emph{mOSaic\_emis2014} ($6\,\unit{Tg}$), however, lies well within the range given by satellites for the years 2005 and 2014 \citep[][Fig.~26]{ESA:Gaudel2018}. This indicates that the Oslo~CTM3 responses resonable to given changes in global emissions despite the strong positive bias in ozone concentrations and accordingly low bias in total dry deposition.
%
\begin{table*}[h]
  \caption{Annual mean tropospheric ozone burden for all experiments and $1 \sigma$ standard deviation.}
  \centering
  \begin{tabular}{lrcl}
    \tophline
    Experiment & \multicolumn{3}{c}{Trop. \chem{O_3}}\\
    &  \multicolumn{3}{c}{(Tg)}\\
    \middlehline
    Wesely\_type & 364 & $\pm$ & 23 \\
    mOSaic & 399 & $\pm$ & 31 \\
    mOSaic\_offLight & 395 & $\pm$ & 30 \\
    mOSaic\_offPhen & 398 & $\pm$ & 31 \\
    mOSaic\_SWVL1 & 399 & $\pm$ & 31 \\
    mOSaic\_ice & 401 & $\pm$ & 31 \\
    mOSaic\_desert & 398 & $\pm$ & 31 \\
    mOSaic\_emis2014 & 405 & $\pm$ & 32 \\
    mOSaic\_hough & 393 & $\pm$ & 30 \\
    \bottomhline
  \end{tabular}
  \label{tab:trop_ozone_burden}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with MACC-reanalysis}
\label{subsec:macc}
In this section, we conclude the comparison of our results with respect to global ozone by looking at ECWMF's MACC-reanalysis (obtained from \href{https://apps.ecmwf.int/datasets/data/macc-reanalysis/levtype=ml/}{ECWMF's data center}) \citep{MACC-II}.
In Fig,~\ref{fig:macc_o3conc}, we compare \emph{mOSaic} ozone concentrations in the lowermost model level with surface concentrations deduced from the MACC-reanalysis for the year 2005. The MACC-reanalysis displays low ozone concentrations above all land masses except for the Greenland ice sheet. The lowest values are found in the deep tropics (e.g. northern South America and central Africa), while the highest values occur within $(25-60)\,\unit{^\circ N}$ over the oceans. These values over the oceans are relatively well reproduced by \emph{mOSaic} ($\pm 20\,\unit{\%}$). Over, e.g., South America, central and southern Africa, the Arabian penisula, and the north-western Indian subcontinent, the ozone concentrations are elevated by up to $200\,\unit{\%}$. While on global average much more concise with the MACC-reanalysis, \emph{Wesely\_type} displays a similar tendency with respect to elevated ozone over continents, especially the deep tropics and the north-western Indian subcontinent (Supplement~S.8) which coincides with regions of high intensity in incoming UV radiation. This may indicated an imbalance in the photo-chemical production and loss of \chem{O_3} in the Oslo~CTM3.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conclusions[Summary and conclusions]  %% \conclusions[modified heading if necessary]
\label{sec:conc}
We have presented an update of the dry deposition scheme in the Oslo~CTM3 from purely prescribed dry deposition velocities \citep{AE:Wesely1989,JGR:Hough1991} to a more process-oriented parameterization taking the state of the atmosphere and vegetation into account. Based on the describtion of dry deposition in \citet{WASP:Simpson2003,ACP:Simpson2012}, we have implemented a moasic approach to compute contributions to dry deposition by individual sub-grid land surface types. Aerodynamic, quasi-laminar, and surface resistance (latter divided into stomatal and non-stomatal contributions) are calculated for each land surface category seperately. Based on these, a landfraction-weighted mean is deduced. In addition, the various dry deposition velocities are now directly available from model output for diagnostics and further studies.

@@

Future work on the Oslo~CTM3 should resolve the ozone high-bias which may invlove revising the photolysis- and chemical reaction computation as well as reaction rates should. For a better modeling of ozone abundances, ocean emissions of very short-lived ozone depleting substances (VSLS) \citep{JGR:Warwick2006, ACP:Ziska2013, ACP:Hossaini2016, ACP:Falk2017} which affect the stratospheric ozone abundance and a scheme covering actic spring-time ozone depletion \citep[][e.g.,]{ACP:Yang2010, ACP:Toyota2011, GMD:Falk2018}, could be worthwhile implementing. The model performance could also be improved by allowing for more plant functional types and phenologies than currently used or implementing an actual photosynthesis-based modeling of plants.

@@

\begin{acknowledgements}
  This work was supported by the Norwegian Research Council (NRC) through the project The double punch: Ozone and climate stresses on vegetation (268073).\\
  The simulations were performed on resources provided by UNINETT Sigma2 -- the National Infrastructure for High Performance Computing and Data Storage in Norway (project nn2806k).\\
  The used Leaf Area Index (LAI) and roughness length ($z_0$) are available online from Oak Ridge National Laboratory Distributed Active Archive Center, Oak Ridge, Tennessee, U.S.A. (\doi{10.3334/ORNLDAAC/970}).\\
  Community Emission Data System (CEDS) historical emission inventory is provided by the Joint Global Research Institute project (\url{http://www.globalchange.umd.edu/ceds/}.)
  Randerson, J.T., G.R. van der Werf, L. Giglio, G.J. Collatz, and P.S. Kasibhatla. 2018. Global Fire Emissions Database, Version 4, (GFEDv4). ORNL DAAC, Oak Ridge, Tennessee, USA. https://doi.org/10.3334/ORNLDAAC/1293
  We would like to thank Prof. Frode Stordal (Section for Meteorology and Oceanography, University of Oslo) for discussions regarding early drafts of the manuscript as well as Anne Fouilloux (scientific programmer at the same institute) for technical support.
  We would also like to thank the Center for International Climate Research (CICERO) for their support of this work.
\end{acknowledgements}

>>>>

\subsubsection{Aerodynamic resistance}
\label{subsubsec:Ra}
In general, the aerodynamic resistance describes the turbulent transport of any substance down to the surface. To derive $R_a^k$, we follow \citet{WASP:Simpson2003,ACP:Simpson2012} and compute a local friction velocity at reference height $z_\mathrm{ref}$ \citep[Eq.~(52),][]{ACP:Simpson2012}
\begin{equation}
  u_*^k = \frac{\overline{u}(z_\mathrm{ref})\cdot\kappa}{\ln{(\frac{z_\mathrm{ref}-d_k}{z_0^k})}-\Psi_m(\frac{z_\mathrm{ref}-d_k}{L})+\Psi_m(\frac{z_0^k}{L})},
  \label{eq:local_fric_vel}
\end{equation}
with the average wind speed $\overline{u}(z_\mathrm{ref})$ at reference height, the K\'{a}rm\'{a}n constant $\kappa = 0.40$, the integrated stability equation for momentum $\Psi_m$ \citep[e.g.,][]{Garratt1992}, a grid average Obukhov length $L$, deplacement height $d_k$, and roughness length $z_0^k$ ($d_k=0.78\cdot h_k(\mathrm{lat})$, $z_0^k=0.07\cdot h_k(\mathrm{lat})$ for forests, $d_k=0.7\cdot h_k(\mathrm{lat})$, $z_0^k=0.1\cdot h_k(\mathrm{lat})$ for vegetation other than forests). Considering the height of vegetation, we have chosen the model level such that $\overline{z}_\mathrm{ref}\approx 45\,\unit{m}$. Using the derived $u_*^k$ from Eq.~(\ref{eq:local_fric_vel}), a local Obukhov length $L_k$ can be obtained from \citep[Eq.~(8),][]{ACP:Simpson2012}:
\begin{equation}
  L_k = - \frac{\rho c_p T_\mathrm{2m} u_*^k}{\kappa g H}.
\end{equation}
Herein, $H$ is the sensible heat flux, $g$ is the standard gravitational acceleration, $c_p$ the specific heat capacity, and $T_{2m}$ the $2\,\unit{m}$ temperature. With these, we can compute the aerodynamical resistance for each land surface type \citep[Eq.~(8.8),][]{WASP:Simpson2003}
\begin{equation}
  R_a^k = \frac{1}{\kappa u_*^k}\left[{\ln{\left(\frac{z_\mathrm{ref}-d_k}{z_0^k}\right)}-\Psi_h\left(\frac{z_\mathrm{ref}-d_k}{L_k}\right)+\Psi_h\left(\frac{z_0^k}{L_k}\right)}\right],
\end{equation}
with the integrated stability equation for heat $\Psi_h$ \citep[e.g.,][]{Garratt1992}. Both integrated stability functions ($\Psi_m$, $\Psi_h$) and corresponding parameters are listed in supplement~S.1.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-laminar layer resistance}
\label{subsubsec:Rb}
The quasi-laminar layer resistance $R_b^{i,k}$ is species specific and differs over land and ocean surfaces.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over land, we use \citep[Eq.~(53),][]{ACP:Simpson2012}
\begin{equation}
  R_b^{i,k} = \frac{2}{\kappa u_*} \cdot \left(\frac{\text{Sc}_i}{\text{Pr}}\right)^{\frac{2}{3}},
  \label{eq:Rb}
\end{equation}
wherein $\text{Pr}$ is the Prandtl number (0.72 for air and other gases) and $\text{Sc}_i$ is the Schmidt number for a gas $i$. Eq.~(\ref{eq:Rb}) differs from a similar formulation in \citet{ACP:Seinfeld2006} by a factor of roughly $1.25$. From $\text{Sc}_i = \nu/D_i$, with the kinematic viscosity of air $\nu$, we derive a Schmidt number in water equivalent:
\begin{equation}
  \text{Sc}_i = \frac{D_\chem{H_2O}}{D_i} \cdot \text{Sc}_\chem{H_2O},
\end{equation}
with the molecular diffusivity for any gas $D_i$, the Schmidt number of water ($\text{Sc}_\chem{H_2O}=0.6$) and its molecular diffusivity ($D_\chem{H_2O}=0.21\cdot10^{-4}\,\unit{m^2\,s^{-1}}$). The used ratios $D_\chem{H_2O}/D_i$ are taken from \citet[][Table S18]{ACP:Simpson2012}.\\

@@

Dry deposition velocities are directly available only for the new model version. For \emph{Wesely\_type}, monthly averaged dry deposition velocities $v^\chem{O_3}_\text{DD}$ had to be retrospectively estimated from the ratio between the total ozone dry deposition $\sum \chem{O_3^\text{DD}}(z_0)$ and monthly averaged ozone amount in the lowermost model level $\chem{O_3}(p_0)$ 
\begin{equation}
  v^\chem{O_3}_\text{DD} = \frac{\sum \chem{O_3^\text{DD}}(z_0)}{\chem{O_3}(p_0)}\cdot c_\text{month}.
  \label{eq:retro_vdd}
\end{equation}
Herein, $c_\text{month} = \frac{\Delta h_\text{month}}{s_\text{month}}$, with the monthly average height of the lowermost model level in each gridbox $\Delta h_\text{month}$ and the respective number of seconds in a month $s_\text{month}$. In case of \emph{mOSaic}, Eq.~(\ref{eq:retro_vdd}) yields similar values for $v^\chem{O_3}_\text{DD}$ as directly available from model output.
%
\subsubsection{Zonal distribution}
\label{subsubsec:zonal}
%
The annual zonal average with respect to surface ozone concentration (Fig.~\ref{fig:mmm_drydep}a) displays on average, in consistency with Fig.~\ref{fig:diff_maps}a, a global increase of surface ozone concentrations by $6\,\unit{ppb}$ comparing \emph{mOSaic} to \emph{Wesely\_type}. This increase is largest in the zonal band $(25-50)\,\unit{^\circ N}$ which contains the major deserts. In the deep tropics ($5\,\unit{^\circ S}-5\,\unit{^\circ N}$), the increase is smallest ($\mathcal{O}(5\,\unit{ppb})$). We find that the mOSaic scheme further intensifies the strong asymmetry between northern and southern hemisphere as a consequence of the distribution of the continental land masses and vegetation thereon. Among the sensitivity studies focusing on the stomatal conductance, there is only a low absolute variance. Neglecting the dependence on light in the stomatal conductance formulation (\emph{mOSaic\_offLight}) -- or in other words allowing photosynthesis 24/7 -- decreases the ozone concentration by $1-2\,\unit{ppb}$ in the tropics and NH mid latitudes, while choosing soil water at shallower depths (\emph{mOSaic\_SWVL1}) increases $[\chem{O_3}]$ insignificantly. Rather surprisingly, switching off the phenology completely (\emph{mOSaic\_offPhen}) amounts on average only to small difference ($\mathcal{O}(<1\,\unit{ppb})$). Most remarkable, but expected due to the much smaller prescribed dry deposition velocity over ice and snow, \emph{mOSaic\_ice} displays a doubling of surface ozone in the high Arctics compared to \emph{Wesely\_type} ($\mathcal{O}(20\,\unit{ppb})$) but affects ozone concentrations down to latitudes at about $50\,\unit{^\circ}$ in both hemispheres. Reducing $R^\chem{O_3}_\text{desert}$ by $60\,\unit{\%}$ (\emph{mOSaic\_desert}) a reduction in the order of $1\,\unit{ppb}$ is found mainly limited to the NH. The largest impact on ozone concentrations ($\mathcal{O}(2-5\,\unit{ppb})$) is found for the experiment \emph{mOSaic\_hough} which is closest to \emph{Wesely\_type}, since we used on average the same $R^\chem{O_3}$ (see Supplement~S.7). The scenario of differing emissions (2005 in comparison to 2014 or more specifically \emph{mOSaic} compared to \emph{mOSaic\_emis2014}), yields higher ozone concentrations in the northern hemisphere in 2005 in accordance to a reduction in sulfur and \chem{NO_x} emissions in south east Asia in later years. An opposite tendency is seen for latitudes south of $30\,\unit{^\circ N}$, where an increase in ozone precursors is seen in CEDS.

@@

Table~\ref{tab:trop_ozone_burden} displays the average tropospheric ozone burden for all model experiments. Consistently with the previous findings, the mOSaic scheme increases the tropospheric ozone burden by about $35\,\unit{Tg}$. From various satellite ozone retrieval products, \citet[][Tab.~5]{ESA:Gaudel2018} deduce a lower limit estimate for global tropospheric ozone burden for the years $2010-2014$ of $333-345\,\unit{Tg}$, but remark that this amount underestimates the actual tropospheric ozone burden, since it is only based on daytime retrievals. Nevertheless, the results of \emph{mOSaic} lie $17\,\unit{\%}$ above that estimate and also well above the typical modeling range of $302-378\,\unit{Tg}$ \citep{ACP:Young2013}. The difference between \emph{mOSaic} and \emph{mOSaic\_emis2014} ($6\,\unit{Tg}$), however, lies well within the range given by satellites for the years 2005 and 2014 \citep[][Fig.~26]{ESA:Gaudel2018}. This indicates that the Oslo~CTM3 responses reasonable to given changes in global emissions despite the strong positive bias in ozone concentrations and accordingly low bias in total dry deposition.
%
\begin{table*}[h]
  \caption{Annual mean tropospheric ozone burden for all experiments and $1 \sigma$ standard deviation.}
  \centering
  \begin{tabular}{lrcl}
    \tophline
    Experiment & \multicolumn{3}{c}{Trop. \chem{O_3}}\\
    &  \multicolumn{3}{c}{(Tg)}\\
    \middlehline
    Wesely\_type & 364 & $\pm$ & 23 \\
    mOSaic & 399 & $\pm$ & 31 \\
    mOSaic\_offLight & 395 & $\pm$ & 30 \\
    mOSaic\_offPhen & 398 & $\pm$ & 31 \\
    mOSaic\_SWVL1 & 399 & $\pm$ & 31 \\
    mOSaic\_ice & 401 & $\pm$ & 31 \\
    mOSaic\_desert & 398 & $\pm$ & 31 \\
    mOSaic\_emis2014 & 405 & $\pm$ & 32 \\
    mOSaic\_hough & 393 & $\pm$ & 30 \\
    \bottomhline
  \end{tabular}
  \label{tab:trop_ozone_burden}
\end{table*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with MACC-reanalysis}
\label{subsec:macc}
In this section, we conclude the comparison of our results with respect to global ozone by looking at ECWMF's MACC-reanalysis (obtained from \href{https://apps.ecmwf.int/datasets/data/macc-reanalysis/levtype=ml/}{ECWMF's data center}) \citep{MACC-II}.
In Fig,~\ref{fig:macc_o3conc}, we compare \emph{mOSaic} ozone concentrations in the lowermost model level with surface concentrations deduced from the MACC-reanalysis for the year 2005. The MACC-reanalysis displays low ozone concentrations above all land masses except for the Greenland ice sheet. The lowest values are found in the deep tropics (e.g. northern South America and central Africa), while the highest values occur within $(25-60)\,\unit{^\circ N}$ over the oceans. These values over the oceans are relatively well reproduced by \emph{mOSaic} ($\pm 20\,\unit{\%}$). Over, e.g., South America, central and southern Africa, the Arabian peninsula, and the north-western Indian subcontinent, the ozone concentrations are elevated by up to $200\,\unit{\%}$. While on global average much more concise with the MACC-reanalysis, \emph{Wesely\_type} displays a similar tendency with respect to elevated ozone over continents, especially the deep tropics and the north-western Indian subcontinent (Supplement~S.8) which coincides with regions of high intensity in incoming UV radiation. This may indicated an imbalance in the photo-chemical production and loss of \chem{O_3} in the Oslo~CTM3.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conclusions[Summary and conclusions]  %% \conclusions[modified heading if necessary]
\label{sec:conc}
We have presented an update of the dry deposition scheme in the Oslo~CTM3 from purely prescribed dry deposition velocities \citep{AE:Wesely1989,JGR:Hough1991} to a more process-oriented parameterization taking the state of the atmosphere and vegetation into account. Based on the description of dry deposition in \citet{WASP:Simpson2003,ACP:Simpson2012}, we have implemented a moasic approach to compute contributions to dry deposition by individual sub-grid land surface types. Aerodynamic, quasi-laminar, and surface resistance (latter divided into stomatal and non-stomatal contributions) are calculated for each land surface category separately. Based on these, a land fraction-weighted mean is deduced. In addition, the various dry deposition velocities are now directly available from model output for diagnostics and further studies.

@@

Future work on the Oslo~CTM3 should resolve the ozone high-bias which may involve revising the photolysis- and chemical reaction computation as well as reaction rates should. For a better modeling of ozone abundances, ocean emissions of very short-lived ozone depleting substances (VSLS) \citep{JGR:Warwick2006, ACP:Ziska2013, ACP:Hossaini2016, ACP:Falk2017} which affect the stratospheric ozone abundance and a scheme covering arctic spring-time ozone depletion \citep[][e.g.,]{ACP:Yang2010, ACP:Toyota2011, GMD:Falk2018}, could be worthwhile implementing. The model performance could also be improved by allowing for more plant functional types and phenologies than currently used or implementing an actual photosynthesis-based modeling of plants.

@@

\begin{acknowledgements}
  This work was supported by the Norwegian Research Council (NRC) through the project The double punch: Ozone and climate stresses on vegetation (268073).\\
  The simulations were performed on resources provided by UNINETT Sigma2 -- the National Infrastructure for High Performance Computing and Data Storage in Norway (project nn2806k).\\
  The used Leaf Area Index (LAI) and roughness length ($z_0$) are available online from Oak Ridge National Laboratory Distributed Active Archive Center, Oak Ridge, Tennessee, U.S.A. (\doi{10.3334/ORNLDAAC/970}).\\
  Community Emission Data System (CEDS) historical emission inventory is provided by the Joint Global Research Institute project (\url{http://www.globalchange.umd.edu/ceds/}.)
  Randerson, J.T., G.R. van der Werf, L. Giglio, G.J. Collatz, and P.S. Kasibhatla. 2018. Global Fire Emissions Database, Version 4, (GFEDv4). ORNL DAAC, Oak Ridge, Tennessee, USA. https://doi.org/10.3334/ORNLDAAC/1293
  We would like to thank Prof. Frode Stordal (Section for Meteorology and Oceanography, University of Oslo) for discussions regarding early drafts of the manuscript, Anne Fouilloux (scientific programmer at the same institute) for technical support as well as Olimpia Bruno (Karlsruhe Institute of Technology) and Franziska Hellmuth (University of Oslo) for valuable input regarding the aerodynamic resistance formulation.
  We would also like to thank the Center for International Climate Research (CICERO) for their support of this work.
\end{acknowledgements}
